TacticToe: Learning the Game of Tactics

### 2018-01-30 tactictoe_jv.tex
minor

\section{Preliminaries: Search Tree}\label{sec:prelim}
\todoi{Print words correctly in math format by avoiding math format}

@@

To facilitate the description  of our algorithms we make a slight adjustement 
to the definition of an open goal. If a node $a$ does not contain any open 
goal, the first pending goal (according 
to some preset order) of $a$ is also considered to be an open goal. In this 
way, each unsolved node contains a unique open goal.
\end{definition}

@@

\begin{definition} (Productive tactic) 
The application of a tactic on an open goal is called productive if and only if 
all the following conditions are satisified:
\begin{itemize}
\item It does not fail or timeout. To prevent tactics from looping, we 
interrupt tactics after a short amount of time (0.05 seconds). 
\item It does not loop. Its output does not contain any goals that appears in 
its ancestor nodes.
\item It is not a parallel step. Its output is not equal or a superset 
of a list of goals produced from the same open goal.
\end{itemize}

@@

@@

An active node is by definition a node that is not a descendant of a 
solved node. Non-active nodes are not worth exploring.

\end{definition}

@@

\section{Comparison with Human Proofs}
\todoi{Test tactictoe find new examples on new goals and manual exploration 
mode.}

>>>>

\section{Proof Search Tree}\label{sec:prelim}

@@

To facilitate the description  of our algorithms we make a slight adjustment 
to the definition of an open goal. If a node $a$ does not contain any open 
goal, the first pending goal (according 
to some preset order) of $a$ is also considered to be an open goal. In this 
way, each unsolved node contains a unique open goal.
\end{definition}

@@

\begin{definition} (Productive tactic) 
The application of a tactic on an open goal is called productive if and only if 
all the following conditions are satisfied:
\begin{itemize}
\item It does not fail or timeout. To prevent tactics from looping, we 
interrupt tactics after a short amount of time (0.05 seconds). 
\item It does not loop. Its output does not contain any goals that appears in 
its ancestor nodes.
\item It is not a parallel step. Its output is not equal or a superset 
of a list of goals produced from the same open goal.
\end{itemize}

@@

some text to add here.

@@

An active node is by definition a node that is not a descendant of a 
solved node. Non-active nodes are not worth exploring.
\end{definition}

@@

\section{Case Study}
\todoi{Test tactictoe find new examples on new goals and manual exploration 
mode.}
In this section, we compare \tactictoe proof script with human proof script.
